\subsection{Denial-of-Service Attacks}\label{text:dos}
\begin{comment}

DoS attacks continues to plague internet services even if they are efficaciously protected against intrusive security breaches, as evidenced by the recent attack on Spamhaus \cite{BBC}. A denial of service attack is essentially a targeted effort to prevent a service from servicing legitimate requests by draining the underlying computer resources.Such an attack is executed by having each attacking machine performing only small load of the total work, relying on the cumulative work to overload the target system. 
\\
\\
A DoS attack can generally be divided into two types of strategies:

\textbf{\emph {Brute force attacks}}



The typical DoS attack exploits the server by generating excessive memory and/or CPU utilisation of the server. Popular examples include SYN spoofing attacks which triggers the server to allocate input buffers for connections that never complete initiation as well as SSL attacks in which the server CPU is overloaded with expensive public-key decryption calculations. 
\end{comment}

\subsection{Proof-of-Work}\label{text:pow}


The fundamental property of Proof of Work is that its \emph{puzzles} are moderately hard to compute but easy to verify. This concept was originally proposed by \citeauthor{DworkN92} 1992 in \citetitle{DworkN92} as a way to counter e-mail spam by increasing the costs of sending spam, thus making e-mail spam economically unfeasible. \citeauthor{DworkN92} originally called this a \emph{pricing function} since it effectively puts a price on using a service.

\begin{GrayBox}[0.75\textwidth]
Impose each request with a cost (e.g. show proof of work to access a service )
\end{GrayBox}

The concept of proof-of-work was reinvented by \citeauthor{Back02}, who later proposed ''hashcash'' as a DoS preventing method in \citetitle{Back02}. Back's idea was to require the requester of a service to compute a cryptographic hash in which the most significant bits start with a certain number of zeroes. \footnote{In the first scheme of \emph{hashcash} the initial bits of two hashes had to match - what mentioned in the text is actually a recent improvement.} Consequently, the average work to solve a ''hashcash'' puzzle is exponential to number of zero bits required vis-à-vis computing a single hash to verify\cite{bitcoin}.

The idea of proof-of-work has since then been adapted into various field such as mitigating denial-of-service attacks \cite{mankins}, limiting the rate of new TCP connections \cite{JuelsB99} and as inducement in peer-to-peer networks\cite{bitcoin,p2p}.




%One of the most significant threats in server security are Denial of Service (DoS) attacks. It is essentially a targeted effort to prevent a service from functioning properly by draining the underlying computer resources. There are different levels of the attacks which either can be targeted to exploit vulnerabilities in the  TCP/IP-protocol, in the operation system that the server runs on or more specific implementations of the service. [källa på det här]


%Researches have shown Proof of Work to have mitigating the effects of a DoS attacks but. To cope with a potential DoS attacks the level of difficulty of the problems is scaled proportionally with the amount stress that is put on the system. [källa på det här]

 % problem would then scale with the The solving of the problem would decrease the rate that each client would be able to issue requests to the server. This reduces the total number of requests that reach the content server in any given timeframe to a level l. l could be tuned to a level lower than the server’s inherent threshold of requests able to execute in said timeframe.

%The Denial of Service (abbr. DoS) is a class of cyber attacks directed to attack the availability of a web service. The typical DoS attack exploits the server by generating excessive memory and/or CPU utilisation of the server. Popular examples include SYN spoofing attacks which triggers the server to allocate input buffers for connections that never complete initiation as well as SSL attacks in which the server CPU is overloaded with expensive public-key decryption calculations. 
			
%One of the big challenges when facing DoS attacks is to distinguish between a legitimate user and an attacker. One approach is to block senders of erroneous packages, but when malicious users pose as legitimate this method certainly fails. The objective is to ensure the availability of the service to the legitimate users without infeasible delays. 
